---
title: "scRNAseq IN Neuron Analysis - GSE140793 - IN Proportion"
author:
  - name: "Emir Turkes"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile, encoding = encoding,
    output_file = file.path(
      "..", "..", "results", unlist(strsplit(getwd(), "/"))[6], "IN_proportion_GSE140793.html"
  ))})
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
div.main-container {max-width: none; width: 100%;}
</style>

*This file is a part of [scRNAseq-IN-neurons](https://github.com/eturkes/scRNAseq-IN-neurons).*

The table of contents in the top left is clickable and can be used to quickly navigate the document.
To toggle the visibility of code, use the `CODE` toggles at the top right of chunks.
The toggle at the start of the document controls the visibility of all chunks.

```{r}
#    This file is part of scRNAseq-IN-neurons.
#    Copyright (C) 2023  Emir Turkes, UK DRI UCL
#
#    This program is free software: you can redistribute it and/or modify
#    it under the terms of the GNU General Public License as published by
#    the Free Software Foundation, either version 3 of the License, or
#    (at your option) any later version.
#
#    This program is distributed in the hope that it will be useful,
#    but WITHOUT ANY WARRANTY; without even the implied warranty of
#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#    GNU General Public License for more details.
#
#    You should have received a copy of the GNU General Public License
#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
#
#    Emir Turkes can be contacted at emir.turkes@eturkes.com

# Load required packages, suppressing startup messages.
# -----------------------------------------------------
packages <- c("conflicted", "Seurat", "patchwork", "DT", "tidyr", "ggplot2")
invisible(suppressPackageStartupMessages(lapply(packages, FUN = library, character.only = TRUE)))
# -----------------------------------------------------

# Define global settings.
# -----------------------
knitr::opts_chunk$set(fig.width = 10, fig.height = 7, dpi = 300)
# -----------------------

# Define functions.
# -----------------
source(file.path("..", "utils.R"))
# -----------------

# Useful variables.
# -----------------
data_name <- unlist(strsplit(getwd(), "/"))[6] # Name of dataset derived from path.

data_dir <- file.path("..", "..", "data", data_name)
cache_dir <- file.path("..", "..", "cache", data_name, "IN_proportion") # Store intermediate data objects here.
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}
# -------------------------------------------------------------------------
```

# IN Proportion Analysis

We look at the proportion of inhibitory neurons in each sample of the dataset below.
Samples were previously processed in separate R Markdown files.

## UMAP Expression Plots with All Cells

Plotting the expression of various IN neuron markers.

```{r}
# Read in files.
# --------------
file_list <- list.files(file.path(cache_dir, ".."), recursive = TRUE) # Processed Seurats stored in cache.
files <- vector("list", length = length(file_list))
for (i in seq_along(files)) {
  files[[i]] <- readRDS(file.path(cache_dir, "..", file_list[i]))
}
# --------------

for (i in seq_along(file_list)) {
  print(
    FeaturePlot(
      files[[i]], features = c("Gad1", "Gad2", "Pvalb", "Sst"), order = TRUE, cols = c("lightgrey", "red")
    ) + plot_annotation( # Title plots with sample name.
      unlist(strsplit(file_list[i], split = "/"))[1],
      theme = theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"))
    )
  )
}
```

# References

This is the concluding section of the document, where we output the `sessionInfo`, and create a bibliography for works cited.

```{r}
sessionInfo()
```
