---
title: "scRNAseq IN Neuron Analysis - GSE189033 - D-2"
author:
  - name: "Emir Turkes"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile, encoding = encoding,
    output_file = file.path("..", "..", "results", unlist(strsplit(getwd(), "/"))[6], "D-2.html")
  )})
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
div.main-container {max-width: none; width: 100%;}
</style>

*This file is a part of [scRNAseq-IN-neurons](https://github.com/eturkes/scRNAseq-IN-neurons).*

The table of contents in the top left is clickable and can be used to quickly navigate the document.
To toggle the visibility of code, use the `CODE` toggles at the top right of chunks.
The toggle at the start of the document controls the visibility of all chunks.

```{r}
#    This file is part of scRNAseq-IN-neurons.
#    Copyright (C) 2023  Emir Turkes, UK DRI UCL
#
#    This program is free software: you can redistribute it and/or modify
#    it under the terms of the GNU General Public License as published by
#    the Free Software Foundation, either version 3 of the License, or
#    (at your option) any later version.
#
#    This program is distributed in the hope that it will be useful,
#    but WITHOUT ANY WARRANTY; without even the implied warranty of
#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#    GNU General Public License for more details.
#
#    You should have received a copy of the GNU General Public License
#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
#
#    Emir Turkes can be contacted at emir.turkes@eturkes.com

# Load required packages, suppressing startup messages.
# -----------------------------------------------------
packages <- c(
  "conflicted", "SingleCellExperiment", "scuttle", "DT", "Seurat", "parallel", "ggplot2", "dplyr", "ggrepel",
  "viridis"
)
invisible(suppressPackageStartupMessages(lapply(packages, FUN = library, character.only = TRUE)))
# -----------------------------------------------------

# Define global settings.
# -----------------------
conflicts_prefer(matrixStats::rowMedians, .quiet = TRUE)

knitr::opts_chunk$set(fig.width = 10, fig.height = 7, dpi = 300)
# -----------------------

# Define functions.
# -----------------
source(file.path("..", "utils.R"))
# -----------------

# Useful variables.
# -----------------
data_name <- unlist(strsplit(getwd(), "/"))[6] # Name of dataset derived from path.
sample_name <- "D-2"

data_dir <- file.path("..", "..", "data", data_name)
cache_dir <- file.path("..", "..", "cache", data_name, sample_name) # Store intermediate data objects here.
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}

protocol <- c("mouse", "droplet", "single-nuc", "umis") # See `cluster_pipeline` in `utils.R`.
vars_to_regress <- NULL # See `cluster_pipeline` in `utils.R`.
parallel_override <- 0 # See `parallel_plan` in `utils.R`.

# Metadata to plot after dimensionality reduction and clustering.
# Values in list can include "no_legend and/or "no_label" to exclude those.
# -------------------------------------------------------------------------
metadata_to_plot <- vector("list", length = 1)
names(metadata_to_plot) <- "seurat_clusters"
# -------------------------------------------------------------------------
```

# Cleaning

We first read in the data and subset to the sample of interest.

```{r}
seurat <- readRDS(file.path(data_dir, "GSM5693472_seurat_unfiltered.rds"))

seurat <- seurat[ , which(seurat$sample == sample_name)] # WT sample.
```

# Cluster Pipeline

We run a pipeline that applies normalization and scaling, dimensionality reduction, and clustering.

```{r}
sub_name <- "all"
seurat <- cluster_pipeline(
  seurat, cache_dir = cache_dir, sub_name = sub_name, protocol = protocol,
  vars_to_regress = vars_to_regress, parallel_override = parallel_override, cc = FALSE, res_divider = 5000
)
seurat

for (i in 1:length(metadata_to_plot)) {
  if ("no_legend" %in% metadata_to_plot[[i]] && "no_label" %in% metadata_to_plot[[i]]) {
    print(
      red_dim_plot(seurat, x = "umap1", y = "umap2", color = names(metadata_to_plot)[i]) +
        NoLegend() +
        ggtitle(names(metadata_to_plot)[i])
    )
  } else if ("no_legend" %in% metadata_to_plot[[i]]) {
    print(
      red_dim_plot(seurat, x = "umap1", y = "umap2", color = names(metadata_to_plot)[i], type = "cat") +
        NoLegend() +
        ggtitle(names(metadata_to_plot)[i])
    )
  } else if ("no_label" %in% metadata_to_plot[[i]]) {
    print(
      red_dim_plot(seurat, x = "umap1", y = "umap2", color = names(metadata_to_plot)[i]) +
        ggtitle(names(metadata_to_plot)[i])
    )
  } else {
    print(
      red_dim_plot(seurat, x = "umap1", y = "umap2", color = names(metadata_to_plot)[i], type = "cat") +
        ggtitle(names(metadata_to_plot)[i])
    )
  }
}

if (protocol[4] == "umis") {
  red_dim_plot(seurat, x = "umap1", y = "umap2", color = "nFeature_SCT", type = "cont") + ggtitle("nFeature_SCT")
  red_dim_plot(seurat, x = "umap1", y = "umap2", color = "nCount_SCT", type = "cont") + ggtitle("nCount_SCT")
} else if (protocol[4] == "reads") {
  red_dim_plot(seurat, x = "umap1", y = "umap2", color = "nFeature_RNA", type = "cont") + ggtitle("nFeature_RNA")
  red_dim_plot(seurat, x = "umap1", y = "umap2", color = "nCount_RNA", type = "cont") + ggtitle("nCount_RNA")
}
```

# References

This is the concluding section of the document, where we output the `sessionInfo`, and create a bibliography for works cited.

```{r}
sessionInfo()
```
