---
title: "scRNAseq IN Neuron Analysis"
author:
  - name: "Emir Turkes"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_file = file.path("..", "results", "analysis.html"))
  })
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
div.main-container {max-width: none; width: 100%;}
</style>

*This file is a part of [scRNAseq-IN-neurons](https://github.com/eturkes/scRNAseq-IN-neurons).*

The table of contents in the top left is clickable and can be used to quickly navigate the document.
To toggle the visibility of code, use the `CODE` toggles at the top right of chunks.
The toggle at the start of the document controls the visibility of all chunks.

# Prep

This section covers necessary but non-directly relevant code for generating the main sections.

```{r}
#    This file is part of scRNAseq-IN-neurons.
#    Copyright (C) 2023  Emir Turkes, UK DRI UCL
#
#    This program is free software: you can redistribute it and/or modify
#    it under the terms of the GNU General Public License as published by
#    the Free Software Foundation, either version 3 of the License, or
#    (at your option) any later version.
#
#    This program is distributed in the hope that it will be useful,
#    but WITHOUT ANY WARRANTY; without even the implied warranty of
#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#    GNU General Public License for more details.
#
#    You should have received a copy of the GNU General Public License
#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
#
#    Emir Turkes can be contacted at emir.turkes@eturkes.com
```

# References

This is the concluding section of the document, where we output the `sessionInfo`, and create a bibliography for works cited.

```{r}
sessionInfo()
```
